Through the eyes of the teacher - Multimodal exploration of expertise differences in the perception of classroom disruptions

### 2022-04-06 02_paper/02_study/paper_methods.Rmd
paper method section

floatsintext      : yes
figurelist        : yes
tablelist         : yes
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

@@

needs(tidyverse,
      lubridate,
      viridis,
      grid,
      gridExtra,
      cowplot,
      readxl,
      ARTofR,
      moments,
      ltm)
```

@@

```{r demographicstable}

# select relevant columns from first questionnaire 
demo.data <- quest.data %>% dplyr::select(LI02_01_1,
                                  LI03_01,
                                  LI04_01,
                                  LI06_05,
                                  LI10_05,
                                  LI11_01,
                                  LI13_01,
                                  LI14
                                  )

# rename columns
demo.data <- rename(demo.data, c("Group" = "LI06_05",
                                 "Gender" = "LI02_01_1",
                                 "Age" = "LI03_01",
                                 "Teaching Experience" = "LI04_01",
                                 "Subject" = "LI10_05",
                                 "Semester" = "LI11_01",
                                 "Internship" = "LI13_01",
                                 "Extracurricular Teaching Experience" = "LI14"
                                 ))

@@

@@

# create a basic table (tibble) using tidyverse functions
demo.table <- demo.data %>%
  group_by(Group) %>%
  summarise(N=n(),
            "Gender female in percentage" = round(sum(Gender/Gender_Sum) * 100, digits = 1),
            "M Age in years" = round(mean(Age), 1),
            "SD Age in years" = round(sd(Age), 1),
            "Min Age in years" = min(Age),
            "Max Age in years" = max(Age),
            "M Exp. in years" = round(mean(`Teaching Experience`), 1),
            "SD Exp. in years" = round(sd(`Teaching Experience`), 1),
            "Min Exp. in years" = min(`Teaching Experience`),
            "Max Exp. in years" = max(`Teaching Experience`),
            "M Semester" = round(mean(Semester), 1),
            "SD Semester" = round(sd(Semester), 1),
            "Min Semester" = min(Semester),
            "Max Semester" = max(Semester),
            "M Internship in teaching units" = round(mean(Internship), 1),
            "SD Internship in teaching units" = round(sd(Internship), 1),
            "Min Internship in teaching units" = min(Internship),
            "Max Internship in teaching units" = max(Internship),
            "Extracurricular Teaching Experience in percentage" = round(sum(`Extracurricular Teaching Experience`/Gender_Sum) * 100, digits = 1),
           )

@@

The expert teachers (`r demo.data %>% filter(Gender == 1 & Group == "Expert") %>% pull(Gender) %>% length()` women; `r demo.table %>% filter(Group == "Expert") %>% pull("Gender female in percentage")`%) had a mean age of `r demo.data %>% filter(Group == "Expert") %>% pull(Age) %>% mean() %>% round(., digits = 1)` years (*SD* = `r demo.table %>% filter(Group == "Expert") %>% pull("SD Age in years") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(Group == "Expert") %>% pull("Min Age in years")`-`r demo.table %>%  filter(Group == "Expert") %>% pull("Max Age in years")`) and an average teaching experience of `r demo.table %>% filter(Group == "Expert") %>% pull("M Exp. in years") %>% mean() %>% round(., digits = 1)` years (*SD* = `r demo.table %>% filter(Group == "Expert") %>% pull("SD Exp. in years") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(Group == "Expert") %>% pull("Min Exp. in years")`-`r demo.table %>%  filter(Group == "Expert") %>% pull("Max Exp. in years")`).

@@

```{r presence_questionnaire}

@@

rownames(quest.table) <- c("Classroom Management", "Balance", "Presence", "Natural Behavior")

@@

@@

One camera was installed to film the class from the side. Two more cameras were installed on the blackboard and at the end of the Lab to film the teacher and class from the front and back. Furthermore, the fourth camera was installed in such a way that only facial expressions and gestures of the teacher were recorded, which enables a semi-automated analysis of the movement sequences.

The Tobii Pro Glasses Controller software was used to record and calibrate the eye movements.

>>>>

floatsintext      : no
figurelist        : yes
tablelist         : yes
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

@@

needs(tidyverse,
      lubridate,
      viridis,
      grid,
      gridExtra,
      cowplot,
      readxl,
      ARTofR,
      moments,
      ltm,
      sjPlot)
```

@@

```{r demographicstable, echo=FALSE}

# select relevant columns from first questionnaire 
demo.data <- quest.data %>% dplyr::select(LI02_01_1,
                                  LI03_01,
                                  LI04_01,
                                  LI06_05,
                                  LI10_05,
                                  LI11_01,
                                  LI13_01,
                                  LI14,
                                  LI18,
                                  LI16_05,
                                  LI17
                                  )

# rename columns
demo.data <- rename(demo.data, c("Group" = "LI06_05",
                                 "Gender" = "LI02_01_1",
                                 "Age" = "LI03_01",
                                 "Teaching Experience" = "LI04_01",
                                 "Type of School" = "LI18",
                                 "Grade" = "LI16_05",
                                 "Subject" = "LI10_05",
                                 "Semester" = "LI11_01",
                                 "Internship" = "LI13_01",
                                 "Extracurricular Teaching Experience" = "LI14",
                                 "Secondary Teaching Activities" = "LI17"
                                 ))

@@

# changing `Secondary Teaching Activities` to count experience (no experience = 2 --> 0)
demo.data$`Secondary Teaching Activities` = ifelse(demo.data$`Secondary Teaching Activities` == 1, "1","0")

# changing character Extra. Exp. into numeric
demo.data$`Secondary Teaching Activities` <- as.numeric(demo.data$`Secondary Teaching Activities`)

@@

# create a basic table (tibble) using tidyverse functions
demo.table <- demo.data %>%
  group_by(Group) %>%
  summarise(N=n(),
            "Gender female in percentage" = round(sum(Gender/Gender_Sum) * 100, digits = 1),
            "M Age in years" = round(mean(Age), 1),
            "SD Age in years" = round(sd(Age), 1),
            "Min Age in years" = min(Age),
            "Max Age in years" = max(Age),
            "M Exp. in years" = round(mean(`Teaching Experience`), 1),
            "SD Exp. in years" = round(sd(`Teaching Experience`), 1),
            "Min Exp. in years" = min(`Teaching Experience`),
            "Max Exp. in years" = max(`Teaching Experience`),
            "M Semester" = round(mean(Semester), 1),
            "SD Semester" = round(sd(Semester), 1),
            "Min Semester" = min(Semester),
            "Max Semester" = max(Semester),
            "M Internship in teaching units" = round(mean(Internship), 1),
            "SD Internship in teaching units" = round(sd(Internship), 1),
            "Min Internship in teaching units" = min(Internship),
            "Max Internship in teaching units" = max(Internship),
            "Extracurricular Teaching Experience in percentage" = round(sum(`Extracurricular Teaching Experience`/Gender_Sum) * 100, digits = 1),
            "Secondary Teaching Activities in percentage" = round(sum(`Secondary Teaching Activities`/Gender_Sum) * 100)
           )

@@

The expert teachers (`r demo.data %>% filter(Gender == 1 & Group == "Expert") %>% pull(Gender) %>% length()` women; `r demo.table %>% filter(Group == "Expert") %>% pull("Gender female in percentage")`%) had a mean age of `r demo.data %>% filter(Group == "Expert") %>% pull(Age) %>% mean() %>% round(., digits = 1)` years (*SD* = `r demo.table %>% filter(Group == "Expert") %>% pull("SD Age in years") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(Group == "Expert") %>% pull("Min Age in years")`-`r demo.table %>%  filter(Group == "Expert") %>% pull("Max Age in years")`) and an average teaching experience of `r demo.table %>% filter(Group == "Expert") %>% pull("M Exp. in years") %>% mean() %>% round(., digits = 1)` years (*SD* = `r demo.table %>% filter(Group == "Expert") %>% pull("SD Exp. in years") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(Group == "Expert") %>% pull("Min Exp. in years")`-`r demo.table %>%  filter(Group == "Expert") %>% pull("Max Exp. in years")`). `r demo.table %>% filter(Group == "Expert") %>% pull("Secondary Teaching Activities in percentage")`% of the experienced teachers were also engaged in an secondary teaching activity, such as lecturers at the university, main training supervisors for trainee teachers and subject advisers.

@@

```{r presence_questionnaire, echo=FALSE}

@@

# rename columns 
rownames(quest.table) <- c("Classroom Management", "Balance", "Presence", "Natural Behavior")

@@

# item analysis of a scale or index using the tab_itemscale() function of the sjPlot package

# Classroom Management
tab_itemscale(quest.data[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)

@@

### 2022-04-06 02_paper/02_study/paper_methods.tex
paper method section

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man,floatsintext]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Through the eyes of the teacher - Multimodal exploration of expertise differences in the perception of classroom disruptions},
  pdfauthor={Mandy Klatt1, Dr.~Gregor Kachel1, 2, Dr.~Christin Lotz1, \& Prof.~Dr.~Anne Deiglmayr1},
  pdflang={en-EN},
  pdfkeywords={Professional Vision, Expert-Novice-Paradigm, mobile Eye-Tracking},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{Professional Vision, Expert-Novice-Paradigm, mobile Eye-Tracking\newline\indent Word count: XXX}
\usepackage{lineno}

@@

The expert teachers (5 women; 71.40\%) had a mean age of 45.10 years (\emph{SD} = 12; range: 27-59) and an average teaching experience of 18.10 years (\emph{SD} = 14.10; range: 3-37).

The novice teachers (13 women; 61.90\%) had a mean age of 23.30 years (\emph{SD} = 1.70; range: 20-27) with an average teaching experience of 0 years. On average, the student teachers were in their 7.40 semester (\emph{SD} = 2.50; range: 3-11). Furthermore, they had an average teaching experience of 12.20 teaching units à 45min (\emph{SD} = 8.40; range: 4-36) through the internships during their studies. 90.50\% of the student teachers were also engaged in an extracurricular teaching activity, such as tutoring or homework supervision.

@@

All reported data analyses were conducted with the R (Version 4.1.2; R Core Team, 2021) and the R-packages \emph{ARTofR} (Version 0.3.3; Zhang, 2021), \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{dplyr} (Version 1.0.8; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 0.5.1; Wickham, 2021), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{lubridate} (Version 1.8.0; Grolemund \& Wickham, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.1; Wickham, Hester, \& Bryan, 2021), \emph{readxl} (Version 1.3.1; Wickham \& Bryan, 2019), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.6; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.2.0; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.3; Barth, 2022), \emph{viridis} (Version 0.6.2; Garnier et al., 2021a, 2021b), and \emph{viridisLite} (Version 0.4.0; Garnier et al., 2021b) and IBM SPSS 28.

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Through the eyes of the teacher - Multimodal exploration of expertise differences in the perception of classroom disruptions},
  pdfauthor={Mandy Klatt1, Dr.~Gregor Kachel1, 2, Dr.~Christin Lotz1, \& Prof.~Dr.~Anne Deiglmayr1},
  pdflang={en-EN},
  pdfkeywords={Professional Vision, Expert-Novice-Paradigm, mobile Eye-Tracking},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{Professional Vision, Expert-Novice-Paradigm, mobile Eye-Tracking\newline\indent Word count: XXX}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

@@

The expert teachers (5 women; 71.40\%) had a mean age of 45.10 years (\emph{SD} = 12; range: 27-59) and an average teaching experience of 18.10 years (\emph{SD} = 14.10; range: 3-37). 71\% of the experienced teachers were also engaged in an secondary teaching activity, such as lecturers at the university, main training supervisors for trainee teachers and subject advisers.

The novice teachers (13 women; 61.90\%) had a mean age of 23.30 years (\emph{SD} = 1.70; range: 20-27) with an average teaching experience of 0 years. On average, the student teachers were in their 7.40 semester (\emph{SD} = 2.50; range: 3-11). Furthermore, they had an average teaching experience of 12 teaching units à 45min (\emph{SD} = 8.60; range: 0-36) through the internships during their studies. 90.50\% of the student teachers were also engaged in an extracurricular teaching activity, such as tutoring or homework supervision.

@@

All reported data analyses were conducted with the R (Version 4.1.3; R Core Team, 2021) and the R-packages \emph{ARTofR} (Version 0.3.3; Zhang, 2021), \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{dplyr} (Version 1.0.8; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 0.5.1; Wickham, 2021), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{lubridate} (Version 1.8.0; Grolemund \& Wickham, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.1; Wickham, Hester, \& Bryan, 2021), \emph{readxl} (Version 1.3.1; Wickham \& Bryan, 2019), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.6; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.2.0; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.3; Barth, 2022), \emph{viridis} (Version 0.6.2; Garnier et al., 2021a, 2021b), and \emph{viridisLite} (Version 0.4.0; Garnier et al., 2021b) and IBM SPSS 28.
